Discrete Quantum Theories and Computing

### 2019-02-13 dissertation.tex
dissertation.lyx Before send Acknowledgments to grammar-checkers...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{csquotes}
\usepackage{comment}
\usepackage{framed}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage{xeCJK}
\setCJKmainfont{SimSun}

@@

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
I learned from the teachers in other courses also helped me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Even if
what taught by my other teachers are not directly related to this
dissertation, I have to thank for your teaching to make me more mature
and easier to communicate with others, especially my English teachers,
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心).
\begin{table}[t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}

Many people have done everything to make my double-major smooth and
to financially support me during my Ph.D. study. I need to thank all
of them, and the complete list of the support according to the employment
and award is listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). In particular,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by the University Information
Technology Services (UITS). The Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service, submitted the Purchase Recommendation Form to suggested IU
libraries to buy them.\todo{Acknowledgments cleaned up until here.
}

Except the financial support via employment and award, I have also
support by my family, especially my father Cheng-Tien Tai (戴振沺). He
always thinks one-step ahead and cares about my future more than I
do. Discussion with other family members and friends also helped me
to compose this dissertation or to do research in general. In particular,
I want to thank Prof.~Daniel Leivant, Prof.~Paul Purdom, Weihua
Liu (刘伟华), and classifies others as the following:\footnote{I only provide the Chinese name for some of them since I only know
their Chinese names and there is no unique way to alphabetize Chinese
into English. Hence, if I randomly choose a way to alphabetize their
name, it might just be a random string which might not be their English
name when they really want to use an English name. For the reader
who don't know Chinese, their names should be able to be copied directly
since the output of \XeLaTeX should be encoded in the Unicode.}

@@

\item The Ph.D. students in Mathematics, including, Kin Wai Chan,
ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
(李盈伟), Yu-Yuan Chen (陳裕元)\ldots{} etc.

\item My other family members, including, my mother Feng-Ming Chang
(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
Caren Liu (劉鈺平) and Kiwi Liu (劉子綺), \ldots{} etc.

\item My official and nonofficial roommates, including Meng-Wei Chen
(陳孟瑋), Yu ``Larry'' Chen (陈煜), Jing-Han Liou (劉經翰), Shu-Ling Wang
(王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).

\item My classmates in NTU, including, Hao-Chun Lee (李浩君), Hsien-Ching
Kao (高憲慶), 鄭維,

\item My building mates, including Chao-Hong Chen (陳昭宏)

\item My other AT\&T family plan members, especially Kexin ``Casey''
Chen (谌可心), Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), for
you always pay our telephone bill on time so that\ldots\ldots\todo{
Maybe I don't have to thank them as AT\&T family plan members, but
I should thank some of them for support and sharing information\ldots}

\item My other roommates,

\item Hao-Chun Lee (李浩君) and for discussing what I did from the perspective
of a general PhD. in Physics and working later in more computational
industry.

@@

\ldots , etc. This could be listed on and on. I still thank you even
if your name is not listed here, and sorry for my bad memory.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{csquotes}
\usepackage{comment}
\usepackage{framed}
\usepackage{mathrsfs}
\usepackage{setspace}
\usepackage{dsfont}
\usepackage[AutoFallBack=true]{xeCJK}
\setCJKmainfont[FallBack=Batang]{SimSun}
% \usepackage{xeCJK}
% \setCJKmainfont{SimSun}

@@

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{bahasai}
\setotherlanguage{basque}
\setotherlanguage{french}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{portuges}
\setotherlanguage{turkish}
\setotherlanguage{vietnamese}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

To have the current content of the dissertation, I would also like
to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
research supervised by Prof.\ Gerardo Ortiz inspired Sec.~\ref{subsec:Maximal-entanglement}
and~\ref{sec:Toward-IVPM}. Besides of my committee members, what
I learned from the teachers in other courses also helped me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Even if
what taught by my other teachers are not directly related to this
dissertation, I have to thank for your teaching to make me more mature
and easier to communicate with others, especially my English teachers,
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心).
\begin{table}[t]
\begin{doublespace}
\noindent \centering{}\caption{\label{tab:teacher}Other courses I took which is relevant to this
dissertation, where IUB stands for Indiana University Bloomington
and NTU stands for National Taiwan University.}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{M{Jin-Tzu~Chen}cM{MATH-M522}Y}
\toprule 
Instructor & School & Course & Relation with the dissertation\tabularnewline
\midrule
\midrule 
Tom Lewis & IUB & SLST-T501 & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper of \emph{Academic Writing}.\tabularnewline
\midrule 
Michael\nolinebreak[3] A. Mandell & IUB & MATH-M522 & The textbook~\cite{Hatcher2001} of \emph{Topology II} is cited
in Chapters~\ref{chap:Introduction} and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline
\midrule 
Steven Myers & IUB & CSCI-B502 & The textbook~\cite{AroraBarak2009} of \emph{Computational Complexity}
is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline
\midrule 
Valery Lunts & IUB & MATH-M501 & The textbook~\cite{DummitFoote2004} of \emph{Survey of Algebra}
is cited in Sec.~\ref{sec:background}, \ref{discretequantumtheoryI},
and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule 
Huah Chu\linebreak[3] (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & The textbook~\cite{Artin1991} of \emph{Algebra (I)} and \emph{(II)}
is cited in Sec.~\ref{CQC1qubitBloch.sec}, \ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline
\midrule
Jin-Tzu Chen\linebreak[3] (陳金次) & NTU & 201~31300 & The textbook~\cite{GAMELIN2003} of \emph{Functions of a Complex Variable}
is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{doublespace}
\end{table}

Many people have done everything to make my double-major smooth and
to financially support me during my Ph.D. study. I need to thank all
of them, and the complete list of the support according to the employment
and award is listed in my Curriculum Vitae at the end of the dissertation.
Most importantly, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
helped me deal with the rules, supervised my reading courses for writing
our papers, and financially support me as a research assistant and
associate. In the department of Mathematics, I need to thank the graduate
services assistant, Kate Forrest, and the directors of graduate study
in Mathematics, especially Prof.\ Christopher Judge, Prof.\ Matthias
Weber, and Prof.\ Michael A.\ Mandell. In the department of Computer
Science, I want to thank the graduate student office; the director
of AI/UI assignments, Charles Pope; the directors of Ph.D. study in
Computer Science, especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}; and the infrastructure and technology group (ITG). In particular,
I don't know how much computational power I consumed to count the
states in Sec.~\ref{subsec:Maximal-entanglement}. These computational
power not only came from the Linux systems in Computer Science but
also came from the Big Red II administrated by the University Information
Technology Services (UITS). The Indiana University Libraries was also
extremely helpful during my dissertation research. Except for a stack
of books I checked out directly, while the books are not in their
collection, I occasionally requested them via the Interlibrary Loan
service, recommended IU libraries to purchase them.

Except the financial support via employment and award, I have also
support by my family, especially my father Cheng-Tien Tai (戴振沺). He
always thinks one-step ahead and cares about my future more than I
do. Discussion with other family members and friends also helped me
to compose this dissertation or to do research in general. In particular,
I want to thank following people which haven't been listed previously:\footnote{I only provide the Chinese name for some of them for three reasons.
First, I might only know their Chinese names. Second, there is no
unique way to translate a Chinese name to English, and I am not familiar
with any of them. Third, all these methods translate infinitely different
Chinese names to the same English name so we loss some precision or
information if we only record their English name.}

@@

\item The Ph.D. students in Mathematics, including Kin Wai Chan,
ChunHsien Lu (呂俊賢), Cong Zhou (周蔥), Junyan Xu (许俊彦), Zhipeng Lu (路志鹏),
Robert Rose, Neal Coleman, Dami Lee, Ruiyu Yang (杨瑞雨), Yingwei Li
(李盈伟), Yu-Yuan Chen (陳裕元), Jan-Li Lin (林展立), Ping Zhong, Chen Xu (徐晨),
Yiqiu Mao (茅一遒), Yu-Min Chung (鍾佑民), Shizhuo Zhang (张诗卓), Max Yining
Zhang (张忆宁), \textturkish{Ata Tuncer}, Hongming Nie (聂洪明), Sandeep
Bhupatiraju, Peng Wang, Guanglu Zhu (祝广路), Sailaja Gajula, Xuqiang
Qin (秦绪强), and \textvietnamese{Phuong Nguyen}, \ldots , etc.

\item Other members in Mathematics, including Weihua Liu (刘伟华),
Yinan ``Christina'' Wu (武怡楠), Cheng ``Freddie'' Shi (史程), Shabnam
Kavousian, and Tyler Bennett (班天瑞), \ldots , etc.

\item My officemates, especially, Inhak Hwang\ (황인학), Jiecao
Chen (陈洁操), Erfan Sadeqi~Azer, Chao ``Alan'' Tao (陶超), Haoyu Zhang
(张皓宇), Yadi Wei (魏雅廸), BoLi Fang (方博立), Yuan Xie (谢缘), and Mrinmoy
Maity, \ldots , etc.

\item My other friends have office in Lindley or \textportuges{Luddy}
Hall, especially, Prof.~Daniel Leivant, Prof.~Paul Purdom, Prof.~Chung-chieh
Shan (單中杰), Chao-Hong Chen (陳昭宏), Robert Rose, \textbasque{Bibrak
Chandio}, Yuxiang Jiang (蒋宇翔), Pei-Ying Chen (陳珮瑩), Prof.~Qin Zhang
(张勤), Kaitlyn Owens, Praveen Narayanan, Liang Chen (陈亮), \textfrench{Ambrose
Bonnaire-Sergeant}, Ali Varamesh, Larry ``LP'' \textfrench{Ailes},
and Min-Chin Lin (林旻瑾), \ldots , etc.

\item My other family members, including, my mother Feng-Ming Chang
(張鳳鳴), my grandmother 戴許玉婷, my sister Sih-Sian Tai (戴司嫻), my cousins
Caren Liu (劉鈺平), and Kiwi Liu (劉子綺), \ldots , etc.

\item My official and nonofficial roommates, including Meng-Wei Chen
(陳孟瑋), Yu ``Larry'' Chen (陈煜), Kenshin Reita (禮田謙信), Jing-Han Liou
(劉經翰), Shu-Ling Wang (王舒齡), and Wan-Ling ``Wynnie'' Chang (張婉鈴).

\item My classmates or friends in NTU, including Hao-Chun Lee (李浩君),
Hsien-Ching Kao (高憲慶), Wei Cheng (鄭維), Chin-Yi Lin (林金毅), Chun-Ting
Chen (陳俊廷), and Prof.~Chenying Huang (黃貞穎), \ldots , etc.

\item My friends lived in the Tulip Tree Apartments, including Chao-Hong
Chen (陳昭宏), Tsaiyi Wu (吳采奕), Cheng ``Freddie'' Shi (史程), Ossama
Abdel~Gawwad, and Cathryn ``Cathy'' Creger-Chambers, \textbahasai{Sary
Silvhiany}, Shaozhuan Li (李绍颛), and Chenwei Zhang (张晨薇), Shu-Nan ``Nancy''
Chang (張舒涵), and Ching-Chi ``Victoria'' Chang (張靖琪), \ldots , etc.

\item My AT\&T family plan members, especially Meng-Wei Chen (陳孟瑋),
Yao-yu Chih (池耀宇), and Xinyi ``Diana'' Gong (龚欣怡), \ldots , etc.

\item Other friends, including Yu-Jung Lin (林宇容), Winnie Lou (何慧芳),
Yi-Rong Yang (楊宜蓉), Yi-Chu Chang (張逸竹), Jim \textgerman[variant=german,spelling=new,babelshorthands=true]{Zimmerly},
Davis Chen (陳鵬舟), Zihang Shao (邵子航), Prof.~Ying Ding (丁颖), Hung-Chun
Chao (趙竑鈞), Guang Zuo (左光), Prof.~Jung-Chao Ban (班榮超), Prof.~Jyh-Chyi
Gong (龔治齊), and 江靜宜, \ldots , etc.

@@

\noindent This list could be on and on and never ends. If you have
help me in any form or provide any helpful information during my Ph.D.
study, but I forget to list you or your unit here. Please forgive
my bad memory.
